RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-03 manuscripts/manuscript.Rmd
Parked paragraph from earlier text.
Fixes up intro to RNeXML package.

`RNeXML` is an R package entirely written in R, and the current stable
version can be installed from the CRAN library[^1]:

@@

@@

>>>>

The `RNeXML` package is written entirely in R and available under a
CC0 public domain waiver. The current development version can be found
on Github at [https://github.com/ropensci/RNeXML](), and the stable
version can be installed from the CRAN repository:

@@

`RNeXML` is part of the rOpenSci project. Users of `RNeXML` are
encouraged to submit bug reports or feature requests in the issues log
on Github, or to contact `ropensci-discuss@googlegroups.com` or the
phylogenetics R users group list at `r-sig-phylo@r-project.org` for
help.

@@

By contrast, the NeXML extension is not only backwards
compatible but contains a precise and machine-readable description of
what it is encoding.
